---
title: "ESM206_Lab8"
author: "Kirsten White"
date: "11/15/2021"
output: html_document
---

```{r setup, include = FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

**Lab 8 Objectives:**

- Explore multivariate data (SLO housing prices)
- Perform multiple linear regression
- Assess diagnostics
- Compare different models by AIC
- Explain model outputs
- Make a nice table of regression results
- Make predictions using a final model
- git branch

```{r packages}
# Install packages

library(tidyverse)
library(corrplot)
library(stargazer)
library(broom)
library(modelsummary)
library(here)
```

### 2. Load data, and filter to only include homes in SLO, Arroyo Grande, Santa Maria-Orcutt, and Atascadero
Read in the data: 

```{r}
# Read in the data 
homes <- read_csv(here("data", "slo_homes.csv"))

```

Create the subset: 

```{r}
# Subset created to only include cities: SLO, Arroyo Grande, Santa Maria-Orcutt, and Atascadero
homes_sub <- homes %>%
  filter(City == "Arroyo Grande" | City == "Santa Maria-Orcutt" | City == "Atascadero" | City == "San Luis Obispo") 
# looks in every row to see if any of these cities appear in the row; could also do: filter(City %in% c("city", "city", etc))
# to make sure this worked: type > unique(homes_sub$City) in the console and make sure only those 4 cities are returned 

```

## Explore data a little bit 
Basic reminders of exploration -> summary stats for (home price, based on city and sale status)

- Find and return in a summary table the mean and standard deviation of home price, grouped by city and status

```{r, include = FALSE, eval = FALSE}
homes_sub_summary <- homes_sub %>%
  group_by(City, Status) %>%
  summarise(mean_price = mean(Price, na.rm = TRUE), 
            sd_price = sd(Price, na.rm = TRUE)) # use na.rm = TRUE to ... []

homes_sub_summary

# Decide I don't even want to run this code, add eval = FALSE; will just skip to next code chunk and run that (used to see if this code chunk is the one having issues)
```
- Add a visualization to explore data to compare home prices vs city 

```{r}
# Plot home prices by city 
ggplot(data = homes_sub, aes(x = Price)) +
  geom_density(aes(color = City, fill = City), alpha = 0.3) + # alpha fills in the lines and make it slightly transparent so you can see layers; alpha is outside aes() because it is not referring to a variable
  scale_x_continuous(limits = c(0, 3e6)) # a way to limit the plot from 0-3 million by setting limits on the x-axis
```

Explore the relationship between square footage and home price (visually) 
```{r}
ggplot(data = homes_sub, aes(x = SqFt, y = Price)) +
  geom_point(aes(color = City, pch = Status), alpha = 0.6) 
```
### Model the relationship as home price as the dependent variable 

```{r}
# make a saturated model (linear regression model) this will include every variable in the data set

homes_lm1 <- lm(Price ~ City + Bedrooms + Bathrooms + SqFt + PricePerSqFt + Status, data = homes_sub) # Determine the price based on ALL variables in data set 

# Make a subset that only contains the quantitative variables (Price through Price/SqFt)

homes_quant <- homes_sub %>%
  select(Price: PricePerSqFt)

# Now find correlation between these

homes_cor <- cor(homes_quant)
homes_cor # returns table indicating correlation between all the values (0 - 1 range) 

# use corrplot to visually see these correlations represented in the table above 

corrplot(homes_cor, method = "ellipse")

# How would I explore the diagnostic plots? 
plot(homes_lm1)

```

# Considering the coefficients returned when typw homes_lm1 into the console: 
- can expect a house in Atascadero to cost ~ -9000 less than a house in Arroyo Grande
- red flag that house price decreases with number of bedrooms (for each additional bedroom in a house, I expect the price to decrease ~ -30000; does not make sense)
- another red flag: regular sale price is negative compared to foreclosure price 
- consider: what [variables] should be removed? 

Let's try another model (homes_lm2) where we simplify this based on our concerns. Include only 3 predictor variables: 
- City
- SqFt
- Status 

```{r}
homes_lm2 <- lm(Price ~ City + SqFt + Status, data = homes_sub)
homes_lm2

# based on this, SLO homes are more expensive while Atascadero and Sm are cheaper than Arroyo Grande; compared to a foreclosed house, regular and short sale homes sell for more and have a higher sq footage 

plot(homes_lm2) # plot diagnostics 
```

Next, lets look at the summary of both of these (in the console: summary(homes_lm1))
- r squared for homes_lm1 (0.8457) -> 84% of variance in home price is explained by the predictor variables in this model (all of them)

Now, looking at the summary for homes_lm2
- r squared value is 0.5268 -> 52% variance in home price is explained by the predictor variables in this model (city, sqft, status)

Which is the best? (least complex, best explanation) -> Use AIC
- higher AIC = worse balance between model fit and complexity 
- lower AIC = better balance between model fit and complexity 

```{r}
AIC(homes_lm1)
AIC(homes_lm2)

# indicates the first model (including all variables) has the best balance. We know this is not true. 
```

Let's try another permutation of this model that we think makes sense. Then check out and compare model fit, outputs, and AIC value. 
```{r}
homes_lm3 <- lm(Price ~ City + SqFt + Bedrooms + Status, data = homes_sub)

plot(homes_lm3)
summary(homes_lm3)
AIC(homes_lm3)
```

## Use 'model summary' to show model outputs side by side: 
- can do this on single model or multiple models
- if you use modelsummary for multiple models you need to input them as a list
```{r}
modelsummary(homes_lm1)
modelsummary(list(homes_lm1, homes_lm2, homes_lm3))

```

